
\section*{Declaration of Originality}

\vspace{0.5cm}

I hereby submit the written work entitled:

\vspace{0.5cm}

\textbf{Perception for playing badminton with a quadruped}

\vspace{0.25cm}

% The following is based on: https://ethz.ch/content/dam/ethz/main/education/rechtliches-abschluesse/leistungskontrollen/declaration-originality.pdf
% In consultation with the supervisor, one of the following three options must be selected.
% Please use the $\blacksquare$ and $\square$ to mark and unmark the option respectively.

% TODO
\begin{itemize}
   % If the following option is selected, then chapter/declaration_generative_ai need not be included:
   \item[$\square$] I hereby declare that I authored the work in question independently, i.e. that no one helped me to author it. Suggestions from the supervisor regarding language and content are excepted. I used no generative artificial intelligence technologies\footnote{For further information please consult the ETH Zurich websites, e.g. \url{https://ethz.ch/en/the-eth-zurich/education/ai-in-education.html} and \url{https://library.ethz.ch/en/researching-and-publishing/scientific-writing-at-eth-zurich.html} (subject to change).}.
   % If the following option is selected, then chapter/declaration_generative_ai MUST be included:
   \item[$\blacksquare$] I hereby declare that I authored the work in question independently. In doing so I only used the authorised aids, which included suggestions from the supervisor regarding language and content and generative artificial intelligence technologies. The use of the latter and the respective source declarations proceeded in consultation with the supervisor.
\end{itemize}

\vspace{0.5cm}

\textbf{Author(s)}

\vspace{0.5cm}

\begin{tabular}{ p{5cm} p{5cm} }
  Florentin & Dipner \\
\end{tabular}

\vspace{0.5cm}

\textbf{Student supervisor(s)}

\vspace{0.5cm}

\begin{tabular}{ p{5cm} p{5cm} }
    Dr. Andrei & Cramariuc\\
    William & Talbot\\
    Turcan & Tuna \\
\end{tabular}

\vspace{0.5cm}

% \textbf{Committee members(s)}
%
% \vspace{0.5cm}
%
% \begin{tabular}{ p{5cm} p{5cm} }
% % TODO Add committee member first/last name
%   First name & Last name \\
% \end{tabular}
%
% \vspace{0.5cm}

\textbf{Supervising lecturer}

\vspace{0.5cm}

\begin{tabular}{ p{5cm} p{5cm} }
  Marco & Hutter \\
\end{tabular}

\vspace{0.5cm}

With my signature I confirm the following:
\begin{itemize}
    \item I have adhered to the rules set out in the \href{https://www.ethz.ch/content/dam/ethz/main/education/rechtliches-abschluesse/leistungskontrollen/plagiarism-citationetiquette.pdf}{Citation Guidelines}
    \item I have documented all methods, data and processes truthfully and fully.
    \item I have mentioned all persons who were significant facilitators of the work.
\end{itemize}

\vspace{0.5cm}

I am aware that the work may be screened electronically for originality.

\vspace{2.75cm}

\begin{tabular}{ p{5cm} p{1cm} p{5cm} }
  \cline{1-1} \cline{3-3}
  Place and date & & Signature \\
\end{tabular}
