\section*{Declaration: Use of Generative AI (GenAI)}

\vspace{1em}

% Checkboxes section
Please declare all uses of Generative AI (GenAI) in your work:

{\scriptsize
\begin{multicols}{2}
\begin{itemize}[label={}, itemsep=0pt, parsep=0pt]
    % Replace $\square$ with $\blacksquare$ when declaring a usage:
    \item[$\square$] \mbox{Text generation (initial version)${}^\ast$}
    \item[$\square$] \mbox{Presentation generation (initial version)${}^\ast$}
    \item[$\square$] \mbox{Generation of figures directly from data${}^\ast{}^\dagger$}
    \item[$\square$] \mbox{Paper research and literature review${}^\ast$}
    \item[$\square$] \mbox{Generation of videos${}^\ast$}
    \item[$\square$] \mbox{Text refinement (incl. Grammarly, Writefull)}
    \item[$\square$] \mbox{Presentation refinement (incl. 365 Copilot)}
    \item[$\square$] \mbox{Code generation/debugging/optimization}
    \item[$\square$] \mbox{Generation of non-data-driven figures}
    \item[$\square$] \mbox{Other (describe below):}
\end{itemize}
\end{multicols}
}
\vspace{-1em}
\fbox{
    \parbox[t][2cm][t]{\textwidth}{
        \vspace{0.5em}
        \hspace{0.5em} % Start some margin inside the box
        % Add description here.
    }
}

{\footnotesize
${}^\ast$ For the uses designated, supplementary material (e.g., as an appendix) containing all prompts and responses must be provided with your final submission.
}

\vspace{2em}

% Signature section
\noindent
\textbf{Signature:} \rule{5cm}{0.4pt} \hfill \textbf{Date:} \rule{3cm}{0.4pt}

\vspace{2em}

% Guidelines
\textbf{Our Guidelines:}
\noindent
\begin{itemize}[itemsep=3pt, parsep=0pt]
    \item You are responsible for the content of the work you submit.
    \item Do not upload copyrighted, private, or confidential information to GenAI tools.
    \item Do not copy/paste generated text, data, or code before careful revision.
    \item Triple-check any generated citations or sources. You must have checked all the works you cite.
    \item When using GenAI for research or ideation, ensure that you understand the output within the context of your work and discuss with supervisors if the validity is unclear. Do not blindly accept the output.
    \item $^{\dagger}$Instead of using GenAI to generate figures or plots from data, prefer to use it to assist in the creation of code that generates them. This way the figures or plots are reproducible and verifiable.
\end{itemize}

% \vspace{1em}

% Resources
\textbf{Additional Resources:}
\noindent
\begin{itemize}[itemsep=3pt, parsep=0pt]
    \item ETH Z\"urich \textit{AI in Teaching and Learning} (\url{https://ethz.ch/en/the-eth-zurich/education/ai-in-education.html}) provides guidelines about responsible, transparent and fair use of GenAI tools.
    \item ETH Z\"urich \textit{Plagiarism and generative Arificial Intelligence (genAI)} (\url{https://library.ethz.ch/en/researching-and-publishing/scientific-writing-at-eth-zurich/plagiat-und-kuenstliche-intelligenz-ki.html}) provides guidelines about the use of GenAI in scientific writing.
    \item ETH Z\"urich \textit{AI Tools \& Licenses} (\url{https://ethz.ch/en/the-eth-zurich/education/ai-in-education/tools.html}) provides recommendations about which GenAI tools should be used and how. For ChatGPT for example, ``It is strongly recommended to \textbf{switch off the option ``Improve the model for everyone"} so that inserted texts and data are not used for training the model".
\end{itemize}
